A Spatial AR System for Wide-area Axis-aligned Metric Augmentation of Planar Scenes

### 2021-09-02 paper/elsarticle/elsarticle-template.tex
paper

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to instructions in paper form or on a screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp an image to be projected in a manner that it, when projected, appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), a cumbersome manual process called keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---can be used to carry out an appropriate corrective image warp. %, since the geometry of the scene as it relates to the geometry of the projector plays a role in how the pixels of the projector's image plane map to points in the scene

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, using a projector equipped with a steerable mirror and a camera facing the scene plane. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) placement of the desired augmentations is carried out in accordance with the axes of an image of the scene acquired by the camera, thereby making setting those axes as simple as appropriately rotating the camera relative to the scene. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby allowing for consistent scaling across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene \cite{schlund2018moglichkeiten,masood2019augmented,gattullo2019towards,uva2018evaluating,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to instructions in paper form or on a screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed typically using some form of head-mounted display. Reliance on head-mounted displays, however, has two adverse consequences: (i) a head-mounted display must be worn by each individual wishing to partake in the augmentation, and (ii) such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. In turn, a form of augmented reality referred to as \textit{spatial} AR\cite{bimber2019spatial} is carried out not by embedding the augmentation in an image of the scene as with a head-mounted display, but by projection to the scene itself, thus eliminating both aforementioned problems. Yet considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions. Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction to appropriately warp the image to be projected, often using software bundled with the projector.

@@

%Mention asymmetrical circle pattern: \cite{chiu2011novel}

%13. X. Zhang and L. Zhu, “Projector calibration from the camera
%image point of view,” Opt. Eng. 48, 117208 (2009).
%14. X. Chen, J. Xi, Y. Jin, and J. Sun, “Accurate calibration
%for a camera-projector measurement system based on
%structured light projection,” Opt. Laser Eng. 47, 310–319
%(2009).
%15. I. Din, H. Anwar, I. Syed, H. Zafar, and L. Hasan, “Projector
%calibration for pattern projection systems,” J. Appl. Res.
%Technol. 12, 80–86 (2014).
%16. R. Orghidan, J. Salvi, M. Gordan, C. Florea, and J. Batlle,
%“Structured light self-calibration with vanishing points,”
%Mach. Vision Appl. 25, 489–500 (2014).
%17. J. Huang, Z. Wang, Q. Xue, and J. Gao, “Calibration of a
%camera-projector measurement system and error impact
%analysis,” Meas. Sci. Technol. 23, 125402 (2012).
%18. W. Gao, L. Wang, and Z. Hu, “Flexible calibration of a portable
%structured light system through surface plane,” Acta Autom.
%Sinica 34, 1358–1362 (2008).
%19. G. Falcao, N. Hurtos, J. Massich, and D. Fofi, “Projectorcamera calibration toolbox,” Technology Report, 2009, available at http://code.google.com/p/procamcalib.
%20. S. Zhang and P. Huang, “Novel method for structured light
%system calibration,” Opt. Eng. 45, 083601 (2006).
%21. F. Berry, O. Aider, and J. Mosnier, “A visual servoing-based
%method for ProCam system calibration,” Sensors 13, 13318–
%13333 (2013).
%22. H. Anwar, I. Din, and K. Park, “Projector calibration for 3D
%scanning using virtual target images,” Int. J. Precis. Eng.
%Manuf. 13, 125–131 (2012).

%todo: It consists of a projector and a small mirror with 2 axes of rotation. In contrast with the present work, Everywhere Displays is limited to projecting on a discrete set of planar surfaces which are calibrated beforehand, each modeled by a 2D homography. The Everywhere Displays project explored many applications of steerable displays, particularly in the retail domain. With the addition of a pan and tilt video camera, a number of gesture-based interactions are demonstrated, including touch-based manipulation of projected graphical widgets [12], as well as person tracking to enable graphics to follow the user. A small number of later works contribute steerable displays designs which mount the projector and camera directly onto motorized platform with pan and tilt axes of motion [8, 6, 11]. Butz et al. [7] contribute a number of interactions in the tradition of ubiquitous computing, such as the ability to

%Automatic Calibration of a Multiple-Projector Spherical Fish Tank VR Display

>>>>

\begin{abstract}
Augmented reality (AR) promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene, potentially reducing or altogether obviating the need for workers to refer to such instructions in paper form or on a statically situated screen. \textit{Spatial} AR, in turn, is a form of AR whereby the augmentation of the scene is carried out using a projector, with the advantage of rendering the augmentation visible to all onlookers simultaneously without calling for any to hold a handheld device such as a tablet or for each to wear some form of head-mounted display. In carrying out spatial AR, however, care must be taken to appropriately warp an image to be projected in a manner that it, when projected, appear free of distortions to the viewer. For planar scene geometry (such as a floor, wall, or table), a cumbersome manual process called keystone correction can be used to carry out an appropriate corrective image warp. Another drawback of conventional spatial AR relying only on a projector is that it is capable of augmenting only the portion of the scene within the projector's own static field of view, thereby hindering its applicability to use cases calling for augmentation of wide areas such as a factory floorspace.

We propose a spatial AR system for wide-area metric augmentation of planar scene surfaces that produces the effect of keystone correction analytically as a function of the relative geometry of the projector and scene plane, using a projector equipped with a steerable mirror to direct the projection across varying target locations and a camera facing the scene plane in support of calibrating the system. Our system renders the placement of augmentations in the scene more intuitive than manual keystone correction in two ways. First, (i) placement of the desired augmentations is carried out in accordance with the axes of an image of the scene acquired by the camera, thereby making setting those axes as simple as appropriately rotating the camera relative to the scene. Second, (ii) the desired dimensions of the projected augmentations are specified in metric terms, thereby allowing for consistent scaling across all target locations. %Our system produces such augmentations accurately, with compelling time savings relative manual keystone correction.
\end{abstract}

@@

Augmented reality (AR) \cite{van2010survey,zhou2008trends} promises to enable use cases in industrial settings that include the embedding of assembly instructions directly into the scene~\cite{schlund2018moglichkeiten,uva2018evaluating,masood2019augmented,gattullo2019towards,aschenbrenner2019comparing,mayrhofer2019one,rupprecht2020information,Rupprecht2021}, potentially reducing or altogether doing away with the need for workers to refer to such instructions in paper form or on a statically situated screen. Typically, AR works by embedding the augmentation in an image of the scene acquired from the viewpoint of a single individual, with the resulting augmented image in turn displayed typically using some form of handheld or head-mounted display. Handheld devices such as tablets do not enable the user to work hands-free while using the device, or force the user to wear additional gear. Reliance on head-mounted displays has two adverse consequences of its own: a head-mounted display must be worn by each individual wishing to partake in the augmentation, and such a head-mounted display---in some cases taking the form of a helmet in order to house multiple sensors in support of accurately tracking the viewpoint of the viewer relative to the scene---can be obtrusive. A Hololens 2, for instance, is such a head-mounted display; at a weight of 566~grams,\footnote{\url{https://www.microsoft.com/en-us/hololens/hardware}} it places an additional ergonomic load on the worker, in particular if worn over a longer duration or in bent positions.

In turn, a form of augmented reality referred to as \textit{spatial} AR\cite{bimber2019spatial} is carried out not by embedding the augmentation in an image of the scene as with a head-mounted or handheld display, but by projection to the scene itself, thus eliminating the aforementioned problems. Spatial AR thus turns surfaces such as the product being manufactured, a desk, the floor, a wall, or even the ceiling (considering overhead work) into displays. Information provision---of the work plan or of quality-related information---can be can be carried out by projection to the given workspace, while directly referring to exact positions within that workspace. Moreover, the fact that this information can be viewed by multiple users simultaneously serves to promote collaboration \cite{aschenbrenner2019comparing}.

While interest in spatial AR in industrial settings has been growing, its deployment in industrial settings remains well behind that of wearable AR systems such as handhelds and head-mounted displays. One of the main shortcomings of typical projector-based spatial AR relative to AR relying on wearables is the applicability of spatial AR only to augmenting scenes within the projector's own static field of view. Here, dynamic projection systems, using mirror heads to deflect the projection across wider areas has the potential to bridge the gap to wider industrial penetration. Yet the increase in the area to be covered comes with noteworthy challenges in terms of ensuring that the images to be projected appear free of distortions to the users. Considering a planar surface to be augmented (e.g., a floor, wall, or table), unless the projector faces the surface frontally, the bounds of a projected rectangular image will not appear rectangular, but will instead be subject to projective distortions. Such distortions can be corrected for by carrying out a cumbersome manual process referred to as keystone correction---involving warping an image by perturbing its corners until the desired effect is produced when projected to the scene---to appropriately warp the image to be projected, often using software bundled with the projector. Automating this manual, time-consuming, and error-prone process significantly reduces the time needed for the industrial engineering of a spatial AR application and therefore has potential to promote adoption by industry. Especially manufacturing processes of large products that remain at a static mounting position during the assembly process---i.e., industrial site assembly---offer a significant application potential for the use of spatial AR as part of worker assistance systems \cite{mayrhofer2019one}.

@@
